% PLEASE USE THIS FILE AS A TEMPLATE
% Check file iosart2x.tex for more examples

% add. options: [seceqn,secthm,crcready,onecolumn]
\documentclass[sw]{iosart2x}
\usepackage{hyperref}
%\usepackage{dcolumn}
%\usepackage{endnotes}

%%%%%%%%%%% Put your definitions here


%%%%%%%%%%% End of definitions

\pubyear{0000}
\volume{0}
\firstpage{1}
\lastpage{1}

\begin{document}

\begin{frontmatter}

%\pretitle{}
%Optimization of fragments sizes for route planning over Linked Connections
\title{Linked Connections: the story so far} 
\runningtitle{Article Title}
%\subtitle{}

% For one author:
%\author{\inits{N.}\fnms{Name1} \snm{Surname1}\ead[label=e1]{first@somewhere.com}}
%\address{Department first, \orgname{University or Company name},
%Abbreviate US states, \cny{Country}\printead[presep={\\}]{e1}}
%\runningauthor{N. Surname1}

% Two or more authors:
\author[A]{\inits{D.}\fnms{David} \snm{Chaves-Fraga}\ead[label=e1]{dchaves@fi.upm.es}},
\author[B]{\inits{J.}\fnms{Julian} \snm{Rojas}\ead[label=e2]{julianandres.rojasmelendez@ugent.be}},
\author[B]{\inits{P.}\fnms{Pieter} \snm{Colpaert}\ead[label=e3]{pieter.colpaert@ugent.be}}
and
\author[A]{\inits{O.}\fnms{Oscar} \snm{Corcho}\ead[label=e4]{ocorcho@fi.upm.es}}
\runningauthor{Chaves-Fraga et al.}
\address[A]{Ontology Engineering Group, \orgname{Universidad Polit\'ecnica de Madrid}, \cny{Spain}}
\address[B]{IDLab, Department of Electronics and Information Systems, \orgname{Ghent University-imec}, \cny{Belgium}
\printead[presep={\\}]{e1,e2,e3,e4}}


\begin{abstract}
Deal with the access and the management of static, but also historical and real-time data, is one of the most relevant problems in several domains which want to take advantage of the benefits of Linked Data. The transport domain is one of these domains but, nowadays, their data are exposing in a way that only ad-hoc systems are able to process them. In previous work, the Linked Connections(LC) framework was introduced as a cost-efficient publishing alternative to the \textit{de-facto} GTFS standard and route planning APIs. At the moment that the route planners take into account real-time and historic data, new issues appear, like for example how we should expose the data on the web, how to improve the query performance or how to ensuring data consistence.

In this paper we present the advances made in the LC framework to deal with real-time and historical data in the transport domain providing a light HTTP interface that allows smart clients to create their own route planners. Our main contribution is a LC server, based on the principles of Linked Data Fragments, that is able to specify the size of each fragment, improving the query evaluation performance and providing a robust access to the data. We also implement the memento protocol in the top of LC and create a new metadata model for improving the discoverability of transport datasets. We evaluate and compare our approach with other possibilities that are also able to deal with real time and historic data. We discover that take into account the size of the fragments has a relevant impact in the performance on the route planning algorithms.   

\end{abstract}

\begin{keyword}
\kwd{Linked Connections}
\kwd{Linked Data Fragments}
\kwd{Transport}
\kwd{Historical Data}
\kwd{Real-time Data}
\kwd{Route Planning}
\end{keyword}

\end{frontmatter}

\input{body}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  ios1.bst will be used to                               %%
%%  create a .BBL file for submission.                     %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\nocite{*} 
% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{ios1}           % Style BST file.
\bibliography{bibliography}        % Bibliography file (usually '*.bib')

% or include bibliography directly:
%\begin{thebibliography}{0}
%\bibitem{r1} F. Author, Information about cited object.
%
%\bibitem{r2} S. Author and T. Author, Information about cited object.
%\end{thebibliography}

\end{document}
